Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 approach.tex

The Conjugate Gradient method is an iterative algorithm for solving symmetric
positive definite systems which runs in $O(n^2\kappa)$ time, where $\kappa$ is
the condition number of the matrix. \scream{Citation for complexity}.

This makes Conjugate Gradient faster than decomposition for matrices with small condition
numbers relative to their size.

@@

As a result, a GPU implementation of conjugate gradient converges in 50
ms when using 250 HOG cells, two orders of magnitude faster than the using
Cholesky factorization with Gaussian Elemination. We report the real time
analysis of whitening using decomposition and conjugate gradient methods in
Fig.~\ref{fig:whotime}.

We compare the speed of each of template generation methods in
Fig.~\cite{fig:covariancetime_crop} Using naive Cholesky decomposition,
WHO template takes several seconds. But, if we use iterative Conjugate Gradient method, it only
takes 100ms. If we use NZ-WHO, we can gain extra speed up since we only whitens non-zero cells.

Also, since the iterative Conjugate Gradient method directly tries to reduce the residual (the norm of $y-Ax$ for $Ax = y$),
it is more numerically stable than Cholesky decomposition with Gaussian Elemination. We vary the number of cells in a template
and show that the residual of NZ-WHO is smaller than WHO Fig.~\ref{fig:whoresidual}.

% Also, the residual from the Conjugate Gradient method (the norm of $y-Ax$ for $Ax = y$) is smaller than 
% that of Cholesky decomposition.

@@

\subsection{High Resolution Templates and FFT based Convolution}
\label{sec:fft} 
We generate high resolution templates with more than 250 HOG cells to capture
details of an object to give accurate 2D-3D matching. These large templates
cause computational burden when computing convolution. Though good for
detecting accurate model and pose, convolution of high-resolution templates are
much slower since computation time scales linearly with the number of HOG
cells in the template. To overcome and speed up the convolution, we used FFT
based GPU convolution \cite{Podlozhnyuk} which scales. Briefly, for length $n$ signal and
length $m$ filter, naive convolution takes $O(nm)$ time whereas FFT-based
convolution takes $O\left( (n + m)\log (n+m) \right)$ time. For large $m$, high
resolution template, we can gain computational advantage.

>>>>

The Conjugate Gradient method is an iterative algorithm for solving symmetric
positive definite systems which runs in $O(n^2\kappa)$ time, where $\kappa$ is
the condition number of the matrix. \scream{Citation for complexity}.
%
This makes Conjugate Gradient faster than decomposition for matrices with small condition
numbers relative to their size.

@@

As a result, a GPU implementation of conjugate gradient converges in 50
ms when using 250 HOG cells, two orders of magnitude faster than the using
Cholesky factorization with Gaussian Elemination.

We report the real time analysis of whitening using decomposition and
conjugate gradient methods in Fig.~\ref{fig:whotime}. (a) compares the
absolute runtime of the different methods while (b) gives the obtained
speedup. We see that % We compare the speed of each of template generation methods in
% Fig.~\cite{fig:covariancetime_crop} Using naive Cholesky decomposition,
WHO template takes several seconds for realistic template sizes of
several hundred cells, while using the iterative Conjugate Gradient
method, it only takes 100ms. If we use NZ-WHO, we can gain extra speed
up since we only whitens non-zero cells.

In addition, since the iterative Conjugate Gradient method directly
tries to reduce the residual (the norm of $y-Ax$ for $Ax = y$), it is
more numerically stable than Cholesky decomposition with Gaussian
Elemination. We vary the number of cells in a template and show that
the residual of NZ-WHO is smaller than WHO Fig.~\ref{fig:whoresidual}.
% Also, the residual from the Conjugate Gradient method (the norm of $y-Ax$ for $Ax = y$) is smaller than 
% that of Cholesky decomposition.

@@

\subsection{High Resolution Templates and FFT based Convolution}
\label{sec:fft} 
We generate high resolution templates with more than 250 HOG cells to capture
details of an object to give accurate 2D-3D matching. These large templates
cause computational burden when computing convolution. Though good for
detecting accurate model and pose, convolution of high-resolution templates are
much slower since computation time scales linearly with the number of HOG
cells in the template. To overcome and speed up the convolution, we used FFT
based GPU convolution \cite{Podlozhnyuk} which scales. Briefly, for length $n$ signal and
length $m$ filter, naive convolution takes $O(nm)$ time whereas FFT-based
convolution takes $O\left( (n + m)\log (n+m) \right)$ time. For large
$m$ (high resolution templates), we can gain computational advantage.
